Final Project Code ALL

### 2022-11-30 Final_Project_Code_ALL.Rmd
office hours

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .88)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

>>>>

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .12)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

```{r}
predict(log_fit, new_data = data.frame(No_of_Votes = 10000, Runtime = 112, IMDB_Rating = 9.8,
                                        Genre_1 = "Drama"), type = "class", threshold = .12
)
```
